Unsupervised embedding of trajectories captures the latent structure of mobility

### 2021-01-14 paper/current/main.tex

%
% CONDITIONAL PROBABILITY EQ
%
\begin{equation}
p(a_{j} \vert a_{i}) = \frac{\exp(\bm{u}_{a_j} \cdot \bm{v}_{a_{i}})}{\sum_{x \in \mathcal{A}} \exp(\bm{u}_{x} \cdot \bm{v}_{a_{i}})},
\end{equation}
where $a_i =a_{t} $, $ a_j=a_{t + \tau}$, $\mathcal{A}$ is the entire set of unique locations represented in the data, and  $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively.
We follow the standard practice and only use the in-vector, $v$,  which is known to be superior to the out-vector in link prediction benchmarks~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}.

>>>>

%
% CONDITIONAL PROBABILITY EQ
%
\begin{equation}
p(j \vert i) = \frac{\exp(\bm{u}_{j} \cdot \bm{v}_{i})}{\sum_{x \in \mathcal{A}} \exp(\bm{u}_{x} \cdot \bm{v}_{i})},
\end{equation}
where $i =a_{t} $, $ j=a_{t + \tau}$, $\mathcal{A}$ is the entire set of unique locations represented in the data, and  $\bm{v}$ and $\bm{u}$ are the ``in-vector" and ``out-vector" respectively.
We follow the standard practice and only use the in-vector, $v$,  which is known to be superior to the out-vector in link prediction benchmarks~\autocite{linzhuo2020hyperbolic, tshitoyan2019mat2vec, garg2018gender, kozlowski2018geometry, hamilton2016diachronic, le2014doc2vec, nakandala2017gendered}.
